Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-03-01 manuscript.tex
Added citations to pandas, mpl, Mayavi

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/tesseroid}
    \caption{
        View of a tesseroid,
        the integration point $Q$ inside the tesseroid,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$,
        and $\ell$ is the Cartesian distance between $P$ and $Q$.
    }
    \label{fig:tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/vary-height-and-order}
    \caption{
        Example of the effect of varying
        the computation height
        and the number of point masses in the Gauss-Legendre Quadrature.
        Black circles represent the horizontal location of the point masses.
        a) $g_{xy}$ calculated at $400\ km$ height using GLQ order 2
        ($2 \times 2 \times 2 = 8$ point masses).
        b) At $150\ km$ height and GLQ order 2,
        the result resembles that of
        four point mases instead of a single tesseroid.
        This effect was shown by \citet{Ku1977}.
        c) At $150\ km$ but with a higher GLQ order of 30,
        the result is similar to that expected for a single mass source.
    }
    \label{fig:glqerrorsample}
\end{figure}

@@

All figures and numerical experiments in this article
were produced by IPython notebooks\footnote{
\href{http://ipython.org}{http://ipython.org}}
\citep{Perez2007}.
These files combine the analysis and figure generation source code
with text, equations, and the figures generated by the code.
The notebook files,
as well as instructions for installing and running the analysis,
are distributed along with the source code archive
that accompanies this article.
Alternatively,
all accompanying material can be downloaded
from an online source code repository\footnote{
\href{https://github.com/pinga-lab/paper-tesseroids}{https://github.com/pinga-lab/paper-tesseroids}}
or a persistent archive\footnote{
\href{}{Zenodo DOI}}.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/tesseroid-split}
    \caption{
        Adaptive discretization
        of the tesseroid shown in (a)
        for a computation point P
        using the distance-size ratio $D$ equal to
        (b) 1, (c) 2, and (d) 6.
        $d$ is the Cartesian distance between
        the center of the top face of the tesseroid
        and $P$.
        $L_r$, $L_\phi$, and $L_\lambda$ are the dimensions of the tesseroid.
        Note that increasing $D$
        results in a fine division of the tesseroid
        close the computation point
        and a coarser division further away.
    }
    \label{fig:division}
\end{figure}

>>>>

% To leave comments on Overleaf
\usepackage[colorinlistoftodos]{todonotes}

@@

\todo[inline]{Here's a comment!}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/tesseroid}
    \caption{
        View of a tesseroid,
        the integration point $Q$ inside the tesseroid,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$,
        and $\ell$ is the Cartesian distance between $P$ and $Q$.
    }
    \label{fig:tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/vary-height-and-order}
    \caption{
        Example of the effect of varying
        the computation height
        and the number of point masses in the Gauss-Legendre Quadrature.
        Black circles represent the horizontal location of the point masses.
        a) $g_{xy}$ calculated at $400\ km$ height using GLQ order 2
        ($2 \times 2 \times 2 = 8$ point masses).
        b) At $150\ km$ height and GLQ order 2,
        the result resembles that of
        four point mases instead of a single tesseroid.
        This effect was shown by \citet{Ku1977}.
        c) At $150\ km$ but with a higher GLQ order of 30,
        the result is similar to that expected for a single mass source.
    }
    \label{fig:glqerrorsample}
\end{figure}

@@

All figures and numerical experiments in this article
were produced by IPython notebooks\footnote{
\href{http://ipython.org}{http://ipython.org}}
\citep{Perez2007}.
These files combine the analysis and figure generation source code
with text, equations, and the figures generated by the code.
We used \textit{pandas} by \citet{Mckinney2010}
to perform the data analysis,
\textit{matplotlib} by \citet{Hunter2007} for graphs,
and \textit{Mayavi} by \citet{Ramachandran2011} for 3D graphs.

The notebook files,
as well as instructions for installing and running the analysis,
are distributed along with the source code archive
that accompanies this article.
Alternatively,
all accompanying material can be downloaded
from an online source code repository\footnote{
\href{https://github.com/pinga-lab/paper-tesseroids}{https://github.com/pinga-lab/paper-tesseroids}}
or a persistent archive\footnote{
\href{}{\todo[inline]{Replace with the Zenodo DOI for the repo.}}}.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/tesseroid-split}
    \caption{
        Adaptive discretization
        of the tesseroid shown in (a)
        for a computation point P
        using the distance-size ratio $D$ equal to
        (b) 1, (c) 2, and (d) 6.
        $d$ is the Cartesian distance between
        the center of the top face of the tesseroid
        and $P$.
        $L_r$, $L_\phi$, and $L_\lambda$ are the dimensions of the tesseroid.
        Note that increasing $D$
        results in a fine division of the tesseroid
        close the computation point
        and a coarser division further away.
    }
    \label{fig:division}
\end{figure}
